Alternative Methods for Implementing Explicit and Finding Implicit Sharing in embedded DSLs

### 2022-12-16 paper/paper.tex
added abstract

% Used for displaying a sample figure. If possible, figure files should
% be included in EPS format.
%
% If you use the hyperref package, please uncomment the following two lines
% to display URLs in blue roman font according to Springer's eBook style:
%\usepackage{color}
%\renewcommand\UrlFont{\color{blue}\rmfamily}
%
\begin{document}
\lstset{language=haskell}
%
\title{Alternative Methods for Implementing
    Explicit and Finding Implicit Sharing in embedded DSLs}
%
\titlerunning{Alternative Explicit and Implicit Sharing}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Curtis D'Alves \and
Christopher Kumar Anand \and
Lucas Dutton \and
Steven Gonder
}
%
\authorrunning{C. D'Alves et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{McMaster University, 1280 Main St W Hamilton, Canada}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
TODO The abstract should briefly summarize the contents of the paper in
150--250 words.

@@

% LocalWords:  DSLs unsafePerformIO Haskell's AST typeclass tagless Trie
% LocalWords:  Kiselyov's haskell consing
% Local Variables:
% LaTeX-verbatim-environments-local: ("minted")
% eval: (setq-local LaTeX-indent-environment-list (cons '("minted" current-indentation) (default-value 'LaTeX-indent-environment-list)))
% End:

>>>>

% Used for displaying a sample figure. If possible, figure files should
% be included in EPS format.
%
% If you use the hyperref package, please uncomment the following two lines
% to display URLs in blue roman font according to Springer's eBook style:
%\usepackage{color}
%\renewcommand\UrlFont{\color{blue}\rmfamily}
%
\begin{document}
\lstset{language=haskell}
%
\title{Alternative Methods for Implementing
    Explicit and Finding Implicit Sharing in embedded DSLs}
%
\titlerunning{Alternative Explicit and Implicit Sharing}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Curtis D'Alves \and
Christopher Kumar Anand \and
Lucas Dutton \and
Steven Gonder
}
%
\authorrunning{C. D'Alves et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{McMaster University, 1280 Main St W Hamilton, Canada}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
  Detection of sharing is known challenge for implementers of embedded domain
  specific languages (DSLs). There are many solutions, each with their
  advantages and drawbacks. Many solutions are based on observable sharing, that
  requires either a monadic interface or use of unsafe referencing, e.g.,
  Data.Reify. Monadic interfaces are consider unsuitable for domain experts, and
  the use of unsafe referencing leads to fragile software.

  Kiselyov's methods for implicit and explicit sharing detection for finally
  tagless style DSLs is an elegant solution without having to resort unsafe
  observable sharing. However these methods are not applicable to all types of
  DSLs (including those generating hypergraphs). We will present alternative
  methods which handle these cases. The main difference comes from the use of a
  trie to perform hashconsing. Our method for implicit sharing essentially
  trades worst-case exponential growth in computation for increased memory
  footprint. To mitigate this issue, our method for explicit sharing reduces the
  memory footprint.

@@

% LocalWords:  DSLs unsafePerformIO Haskell's AST typeclass tagless Trie
% LocalWords:  Kiselyov's haskell consing hypergraphs
% Local Variables:
% LaTeX-verbatim-environments-local: ("minted")
% eval: (setq-local LaTeX-indent-environment-list (cons '("minted" current-indentation) (default-value 'LaTeX-indent-environment-list)))
% End:
